---
title: "git-tips (skills)"
author: "Vishwesha Guttal"
date: "6 October 2015"
output: html_document
---

## Frequently used GIT commands

### Initialize, add, commit 
* Go to the project directory and initlize git.
```{r eval=FALSE}
$ git init
```

* Now add files you want git to track.
     + If you want all files in the directory to be tracked, use: filenames = . 
     + If you want only certain extensions to be tracked, use: filenames = *.desiredextension
     + If you want certain extensions to be ignored, create a file called .gitignore and list all extensions (preceded by *: for example, *.txt)
```{r eval=FALSE}
$ git add filesnames
```


* Commit the changes made for the added filenames
```{r eval=FALSE}
$ git commit -m "First commitment of life"
```

* Now, you can always check the status and logs of all commits with following commands. 

```{r eval=FALSE}
$ git status
$ git log
```

### If you are behind a proxy
* If you are behind a proxy, visit [this link](http://nknu.net/git-through-proxy/) and follow the instructions to add proxy settings to git.

### Move files from computer to github webpage/login
* This following specific step is required only the first time. Move these files to the github server where your login name is gitlogin
```{r eval=FALSE}
$ git remote add origin git@github.com:gitlogin/git-tips.git
$ git push -u origin master
```

* If you now go to http://github.com/gitlogin, you must find your files there! 


### Clone a repository from github webpage to computer
* Follow this link: https://help.github.com/articles/cloning-a-repository/

### Move changed files from computer to webpage
* If you make changes to your files, then the following commands will update the files locally. 
```{r eval=FALSE}
$ git add modifiied-filenames
$ git commit -m "Write key summary of changes here"
```

* Now move it to server
```{r eval=FALSE}
$ git pull -u origin master
$ git push -u origin master
```

* In the above, we first pulled before pushing our changes because if we have collaborators, then those changes must be updated on our files first. 

* When we frequently want to update, we can combine a few commands in one go
```{r eval=FALSE}
$ git add . && git commit -m "Add message here" && git pull -u origin master 
$ git push -u origin master
```

### Reset 


### Branches 


## Useful links

[Learn git commands in 15 minutes](https://try.github.io)

[Git for beginners](http://readwrite.com/2013/09/30/understanding-github-a-journey-for-beginners-part-1)

[Github desktop client](https://desktop.github.com/)
