---
title: "git-tips (skills)"
author: "Vishwesha Guttal"
date: "6 October 2015"
output: html_document
---

## Frequently used GIT commands

### Initialize, add, commit and move to server. 
* Go to the project directory and initlize git.
```{r eval=FALSE}
$ git init
```

* Now add files you want git to track.
     + If you want all files in the directory to be tracked, use: filenames = . 
     + If you want only certain extensions to be tracked, use: filenames = *.desiredextension
     + If you want certain extensions to be ignored, create a file called .gitignore and list all extensions (preceded by *: for example, *.txt)
```{r eval=FALSE}
$ git add filesnames
```


* Commit the changes made for the added filenames
```{r eval=FALSE}
$ git commit -m "First commitment of life"
```

* Now, you can always check the status and logs of all commits with following commands. 

```{r eval=FALSE}
$ git status
$ git log
```

* Now move these files to the github server where your login name is gitlogin
```{r eval=FALSE}
$ git remote add origin git@github.com:gitlogin/git-tips.git
$ git push -u origin master
```

* If you now go to http://github.com/gitlogin, you must find your files there! 

* If you make changes to your files, then the following commands will update the files locally. 
```{r eval=FALSE}
$ git add modifiied-filenames
$ git commit -m "Write key summary of changes here"
```

* Now move it to server
```{r eval=FALSE}
$ git pull -u origin master
$ git push -u origin master
```

* In the above, we first pulled before pushing our changes because if we have collaborators, then those changes must be updated on our files first. 

* When we frequently want to update, we can combine a few commands in one go
```{r eval=FALSE}
$ git add . && git commit -m "Add message here" && git pull -u origin master 
$ git push -u origin master
```

### Reset 


### Branches 


## Useful links

[Learn Git commands in 15 minutes](https://try.github.io)