---
title: "git-tips"
author: "Vishwesha Guttal"
date: "6 October 2015"
output: html_document
---

### Frequently used commands

* In the project directory and type the following set of commands to initlize and 
```{r eval=FALSE}
$ git init
$ git add .
$ git status
$ git commit -m "First committ"
$ git log
$ git remote add origin git@github.com:guttal/git-tips.git
```

* Now move these files to the github server
```{r eval=FALSE}
$ git remote add origin git@github.com:GITLOGIN/git-tips.git
$ git push -u origin master
```

* If you now go to http://github.com/GITLOGIN, you must find your files there! 

* If you make changes to your files, then the following commands will update the files locally. 
```{r eval=FALSE}
$ git add modifiied-filenames
$ git commit -m "Write key summary of changes here"
```

* Now move it to server
```{r eval=FALSE}
$ git pull -u origin master
$ git push -u origin master
```

* In the above, we first pulled before pushing our changes because if we have collaborators, then those changes must be updated on our files first. 

### Useful links

[Learn Git commands in 15 minutes](https://try.github.io)